---
title: "Notes for cue vs uptake vs half-saturation trade-off invasion model (JAM-BSrev)"
author: "K Todd-Brown (ktoddbrown@gmail.com)"
date: '`r Sys.Date()`'
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

TODO: Convert color scheme to wesanderson colorpack

##Set up
```{r setup, message=FALSE}
library(assertthat)
library(reshape2)
library(ggplot2)
library(GGally)
library(plyr)
library(rootSolve)
library(deSolve)
library(knitr)
library(pander)
library(cowplot)

#sourceFiles <- 'R/invasion.R'
#l_ply(sourceFiles, source)

set.seed(100) #reproducible random selection

sessionInfo()
```

#Basic model description
The goal of this model to simulation biologically mediated decomposition. There are two main pools, Substrate ($C$) and Biomass ($B$). Carbon is added to the substrate pool via inputs ($I$), leached from both pools at a rate proportional to the carbon in the pool ($h$ fraction of the biomass pool $B$, and $m$ fraction of the substate pool $C$), and transfer between the substrate $C$ pool and biomass $B$ pool via a reverse Monod uptake with a maximum rate $v$, half-saturation constant $k$, and carbon use effiency $\epsilon$.
Reverse Monod uptake was selected to ensure that both substrate pools were sensitive to changes in inputs.

$\frac{dB}{dt}=\frac{\epsilon vBC}{k+B}-hB$

$\frac{dC}{dt}=I-mC-\frac{vBC}{k+B}$

At steady state ($\frac{dB}{dt}=\frac{dC}{dt}=0$) this implies that:

$B=\frac{Iv\epsilon-mhk}{hv+mh}$

$C=\frac{h}{\epsilon v}(k+B)$


If we further assume that there is a trade off between both 1) uptake $v$ and carbon use effiency ($\epsilon$) such that $v=\frac{e^{b\epsilon}-e^b}{1-e^b}$ and the half saturation constant ($k$) such that $k=a v +k_{min} = \frac{a}{1-e^b}(e^{b\epsilon}-e^b)$. Defined as:


This leads to the following steady state calculations for one biomass pool:

```{r ssOneB}
cue_v_tradeoff <- function(b, vmax, cue){
  return(vmax*(exp(b*cue)-exp(b))/(exp(0)-exp(b)))
}

v_k_tradeoff <- function(kmin, a, v){
  return(kmin+a*v)
}

steadyState <- function(b, vmax, kmin, a, h, m, I, cue){
  v <- cue_v_tradeoff(b=b, vmax=vmax, cue)
  k <- v_k_tradeoff(kmin=kmin, a=a, v=v)

  B <- (I*v*cue-m*h*k)/(h*v+m*h)  
  C <- h/(cue*v) * (k+B)

  return(list(B=B, C=C))
}
```

##Visualize trade-off between cue vs uptake and k
```{r tradeoff_cue_v}

tradeoff.df <- adply(.data=c(-0.1*1:9, -1*1:10, 0.1*1:9, 1:10), .margins=c(1), .id=c('id'), .fun=function(b){
  ans <- data.frame(b=b, cue=seq(0, 1, length=1000))
  ans$v <- cue_v_tradeoff(b=b, vmax=2, cue=ans$cue)
  return(ans)
})

ggplot(tradeoff.df) + geom_line(aes(x=cue, y=v, group=b, color=b))

tradeoff.df$k <- v_k_tradeoff(kmin=0, a=100/2, tradeoff.df$v) #slope is max SOC over vmax range
```

##Steady state sensitivity to inputs

Recall that at steady state:

$B=\frac{Iv\epsilon-mhk}{hv+mh}$

$C=\frac{h}{\epsilon v}(k+B)$

This imples that:
$\frac{dB}{dI}=\frac{v\epsilon}{hv+mh}$
$\frac{dC}{dI}=\frac{1}{v+m}$

#Optimum carbon use effiency
We want the optimum carbon use effiency where biomass is maximum as steady state but that is not possible to solve analytically (you end up with $y=xe^x$, solve for x).
We instead bruite force a solution, iterating $\epsilon$ over $[0,1]$ in incraments of $0.01$

```{r findOptCUE}
optimum_cue <- function(b, vmax, kmin, a, h, m, I){
  cue <- seq(0, 1, length=100)
  ans <- steadyState(b, vmax, kmin, a, h, m, I, cue)
  ans$B[ans$B <= 0 | ans$C <= 0] <- -Inf
  ans$C[ans$B <= 0 | ans$C <= 0] <- -Inf
  
  best <- which.max(ans$B)
  return(list(B_opt=ans$B[best], C_opt=ans$C[best], cue_opt=cue[best]))
}
```

##Generate reasonable parameter sets without compitition
Given that we have input targets between 0.1 and 10 mg-C per g-soil per day, total carbon pools of between 10 to 500 mg-C per g-soil, and a biomass to total carbon ratio of between 0.1 and 15 percent. Let's generate some reasonable parameters to draw on.

```{r resonable, cache=TRUE}
checkPools <- function(B, C){
  return( B > 0 & C > 0 &
    B+C > 10 & B+C < 500 & B/(B+C)> 0.001 & B/(B+C) < 0.15)
}

parm.ls <- list(b=c(-10, -1, -0.1, 0.1, 1, 10),
                vmax=c(0.1, 0.5, 1, 5, 10, 100),
                kmin=c(0, 1, 10, 100, 1000),
                a=c(1/10, 1, 10, 100, 1000),
                h=c(1e-4, 1e-3, 1e-2, 0.1, 1, 10),
                m=c(1e-4, 1e-3, 1e-2, 0.1, 1, 10),
                I=c(0.1, 1, 10))
                
parm.df <- expand.grid(parm.ls)

parm.df <- ddply(parm.df, names(parm.df), function(xx){
  ans <- as.data.frame(optimum_cue(b=xx$b, vmax=xx$vmax, kmin=xx$kmin, a=xx$a, 
              h=xx$h, m=xx$m, I=xx$I))
  return(ans)
})

parm.df$validPools_opt <- checkPools(B=parm.df$B_opt, C=parm.df$C_opt)


ggplot(subset(parm.df, validPools_opt)) + geom_histogram(aes(x=cue_opt))
ggplot(subset(parm.df, validPools_opt)) + geom_violin(aes(x=as.factor(I), y=cue_opt)) 

```

#Competition model co-existance
Consider the senerio where the native popuation is invated by a second competiting population that has a different carbon use effiency but is otherwise equivalent.
Let the strategic carbon use effiency be where the native popuation is never invadable no matter what carbon use effiency value the invader has.

$\frac{dB_i}{dt}=\frac{\epsilon_{i}v_iB_iC}{k_i+B_i}-hB_i$
$\frac{dB_n}{dt}=\frac{\epsilon_{n}v_nB_nC}{k_n+B_n}-hB_n$
$\frac{dC}{dt}=I-mC-\frac{v_nB_nC}{k_n+B_n} - \frac{v_iB_iC}{k_i+B_i}$
where $n$ and $i$ stand for the native and invading populations respectively.

Assume steady state again
$C=\frac{I}{m} - \frac{h}{m}(\frac{B_i}{\epsilon_i} + \frac{B_n}{\epsilon_n})$

$B_i=\frac{\epsilon_i v_i}{h} C - k_i$

Implies that
$(\frac{B_i}{\epsilon_i} + \frac{B_n}{\epsilon_n}) = \frac{v_i}{h} C - \frac{k_i}{\epsilon_i} + \frac{v_n}{h} C - \frac{k_n}{\epsilon_n}$
$(\frac{B_i}{\epsilon_i} + \frac{B_n}{\epsilon_n}) = C \frac{v_n+v_i}{h} - (\frac{k_i}{\epsilon_i} + \frac{k_n}{\epsilon_n})$

Implying that
$mC=I- h(C \frac{v_n+v_i}{h} - (\frac{k_i}{\epsilon_i} + \frac{k_n}{\epsilon_n}))$
$C(m + v_n+v_i)= I + h(\frac{k_i}{\epsilon_i} + \frac{k_n}{\epsilon_n})$
$C = [I + h(\frac{k_i}{\epsilon_i} + \frac{k_n}{\epsilon_n})](m + v_n+v_i)^{-1}$

This requires a new steady state equation
```{r, competeSSFun}
steadyState_compete <- function(b, vmax, kmin, a, h, m, I, cue_i, cue_n){
  v_i <- cue_v_tradeoff(b=b, vmax=vmax, cue_i)
  k_i <- v_k_tradeoff(kmin=kmin, a=a, v=v_i)
  
  v_n <- cue_v_tradeoff(b=b, vmax=vmax, cue_n)
  k_n <- v_k_tradeoff(kmin=kmin, a=a, v=v_n)
  
  C <- (I + h * (k_i/cue_i + k_n/cue_n))/(m + v_n + v_i)
  B_i <- C * cue_i * v_i / h - k_i
  B_n <- C * cue_n * v_n / h - k_n
  
  return(list(C=C, B_i=B_i, B_n=B_n))
}

```

##Strategic CUE
If both CUE are the same then the populations converge to the same biomass at steady state (but are not the same as a single biomass pool because $\frac{1}{k+B_i}+\frac{1}{k+B_n} \neq \frac{1}{k+B_i+B_n}$).
We are looking for the CUE value where, if the invasion cue is only slightly different from the native CUE we minimize the difference between the two biomass pools.

```{r stratCUEFun}
strategic_cue <- function(b, vmax, kmin, a, m, h, I){
  cue <- seq(0, 1, length=100)
  v <- cue_v_tradeoff(b=b, vmax=vmax, cue)
  k <- v_k_tradeoff(kmin=kmin, a=a, v=v)
  
  ans <- steadyState_compete(b, vmax, kmin, a, h, m, I, cue_n=cue, cue_i=cue-0.005)
  
  measure <- abs(ans$B_n-ans$B_i)
  measure[ans$B_n <= 0 | ans$C <= 0] <- Inf
  flag <- which.min(measure)
  
  return(list(cue_strat=cue[flag], C_strat=ans$C[flag], B_strat=ans$B_n[flag]))
}
```

##Tillman
Tillman's R* maximaizes the growth rate. The logic goes something like this. In the strategic solution there exists some $\epsilon_{n}$ such that for all $\epsilon_{i}$, $B_i=0$ and $B_n > 0$.
This is true when the only valid invasion parameterization is equal to the nature population (ie $\epsilon_{n}=\epsilon_{i}$) and is the only solution for $\frac{h}{C}=\frac{\epsilon_n v_n}{k_n+B_n}$, that is CUE is selected to maximize microbial uptake.
```{r tillmanCUEFun}
tillman_cue <- function(b, vmax, kmin, a, m, h, I){
  cue <- seq(0, 1, length=100)
  v <- cue_v_tradeoff(b=b, vmax=vmax, cue)
  k <- v_k_tradeoff(kmin=kmin, a=a, v=v)
  
  ans <- steadyState_compete(b, vmax, kmin, a, h, m, I, cue, cue)
  
  measure <- cue*v/(k+ans$B_n)
  measure[ans$B_n <= 0 | ans$C <= 0] <- -Inf
  flag <- which.max(measure)
  
  return(list(cue_til=cue[flag], C_til=ans$C[flag], B_til=ans$B_n[flag]))
}

```

```{r findTillman, cache=TRUE}
parm.df <- ddply(parm.df, names(parm.df), function(xx){
  return(as.data.frame(tillman_cue(b=xx$b, vmax=xx$vmax, kmin=xx$kmin, 
                        a=xx$a, m=xx$m, h=xx$h, I=xx$I)))
})

parm.df$validPools_til <- with(parm.df, checkPools(B=parm.df$B_til, C=parm.df$C_til))
```


```{r findStrategic, cache=TRUE}
parm.df <- ddply(parm.df, names(parm.df), function(xx){
  return(as.data.frame(strategic_cue(b=xx$b, vmax=xx$vmax, kmin=xx$kmin, 
                        a=xx$a, m=xx$m, h=xx$h, I=xx$I)))
})

parm.df$validPools_strat <- with(parm.df, checkPools(parm.df$B_strat, C=parm.df$C_strat))
```

```{r OptStratPlot}
ggplot(subset(parm.df, validPools_opt & validPools_strat)) + 
  geom_point(aes(y=cue_opt, x=cue_strat)) + 
  geom_abline(slope=1, intercept=c(0), color='grey') +
  labs(y='Optimum CUE (max B w/o compition)', x='Strategic CUE (resistant to invasion)')

ggplot(subset(parm.df, validPools_til & validPools_strat)) + 
  geom_point(aes(y=cue_til, x=cue_strat)) + 
  geom_abline(slope=1, intercept=c(0), color='grey') +
  labs(y='Tillman R* CUE (max B growth)', x='Strategic CUE (resistant to invasion)')
```

#Explore drivers of strategic and optimum differences
```{r exploreDifference}
diff.df <- subset(parm.df, validPools_opt & validPools_strat)

diff.df <- melt(diff.df, measure.vars=names(parm.ls))

ggplot(diff.df) + geom_violin(aes(x=as.factor(value), y=(cue_opt-cue_strat)/cue_opt)) + 
    facet_wrap(~variable, scale='free')
```

We are particullary interested in differences in inputs
```{r exploreInput, cache=TRUE}
validParms <- unique(subset(parm.df, validPools_strat & validPools_opt, 
                     select=c("b", "vmax", "kmin", "a", "h", "m")))
I.arr <- seq(0.1, 10, by=0.3)
Igrad <- ddply(validParms, c("b", "vmax", "kmin", "a", "h", "m"), function(xx){
      ans1 <- ddply(data.frame(xx, I=I.arr), c('I'), function(yy){
        yy1 <- with(data=yy, data.frame(optimum_cue(b, vmax, kmin, a, h, m, I)))
        yy2 <- with(data=yy, data.frame(strategic_cue(b, vmax, kmin, a, h, m, I)))
        if(nrow(yy1) == nrow(yy2)){
          return(cbind(yy1, yy2))
        }else
          return(data.frame())
      })
      ans2 <- ddply(data.frame(xx, I=I.arr*rnorm(length(I.arr), mean=1, sd=0.05)), 
                    c('I'), function(yy){
        yy1 <- with(data=yy, data.frame(optimum_cue(b, vmax, kmin, a, h, m, I)))
        yy2 <- with(data=yy, data.frame(strategic_cue(b, vmax, kmin, a, h, m, I)))
        if(nrow(yy1) == nrow(yy2)){
          return(cbind(yy1, yy2))
        }else
          return(data.frame())
      })
      
      if(nrow(ans1) != nrow(ans2)){
        #print(xx[c("b", "vmax", "kmin", "a", "h", "m"),])
        return(NULL)
      }
      
      dvar <- ans1-ans2
      names(dvar) <- sprintf('d%s', names(dvar))
      
      return(cbind(ans1, dvar))
})
Igrad$validParam <- with(Igrad, checkPools(B=B_opt, C=C_opt)&
                           checkPools(B=B_strat, C=C_strat))
```

```{r plotIgrad}
plot.df <- melt(subset(Igrad, validParam), 
                measure.vars=names(Igrad)[grepl('_(opt)|(strat)', names(Igrad))])
temp <- as.data.frame(matrix(unlist(strsplit(as.character(plot.df$variable), '_|\\.')), ncol=2, byrow=TRUE))
names(temp) <- c('variable', 'type')
plot.df$variable <- NULL
plot.df <- cbind(plot.df, temp)
plot.df$isGrad <- grepl('d', as.character(plot.df$variable))

ggplot(subset(plot.df, isGrad)) + geom_hex(aes(x=I, y=value/dI)) + 
  facet_grid(variable~type, scales='free')

ggplot(subset(plot.df, !isGrad)) + geom_hex(aes(x=I, y=value)) + 
  facet_grid(variable~type, scales='free')
```

#Numerical validation code

Let's pick some points where the gap between the Optimum CUE and Strategic CUE is small ($<20$ percent) and large ($>20$ percent).
```{r pickNumerical}
bigGap.df <- subset(parm.df, validPools_opt & validPools_strat & abs(cue_strat-cue_opt) > 0.2)
smallGap.df <- subset(parm.df, validPools_opt & validPools_strat & abs(cue_strat-cue_opt) < 0.2)

numParm.df <- rbind.fill(bigGap.df[sample.int(nrow(bigGap.df), size=4),],
                         smallGap.df[sample.int(nrow(smallGap.df), size=4),])
numParm.df$index <- 1:nrow(numParm.df)
pander(numParm.df[,c(names(parm.ls), c('cue_opt','C_opt', 'B_opt', 'cue_strat','C_strat', 'B_strat'))])
```

##Validate optimium CUE

```{r validateOpt}
opt.validate <- ddply(numParm.df, c('index', 'C_opt', 'B_opt'), function(xx){
  cue <- seq(0, 1, length=100)
  ans <- steadyState(xx$b, xx$vmax, xx$kmin, xx$a, xx$h, xx$m, xx$I, cue)
  return(data.frame(cue=cue, C=ans$C, B=ans$B))
})

plot.df <- melt(subset(opt.validate, B>0 & C>0), measure.vars=c('C', 'B'))
ggplot(plot.df) + geom_line(aes(x=cue, y=value, group=index)) + 
  geom_vline(data=numParm.df, aes(xintercept=cue_opt)) + 
  facet_grid(variable~index, scales='free')

```

##Validate strategic CUE
```{r validateStrat, warning=FALSE, message=FALSE, results='hide'}
#numParm.df <- subset(parm.df, validPools_opt)
#numParm.df$index <- 1:nrow(numParm.df)
#numParm.df <- subset(numParm.df, index %in% sample(numParm.df$index, size=10))

compitition.model <- function(t, y, parms){
  C <- y[1]; Bn <- y[2]; Bi <- y[3]

  ans <- with(parms,
              c(dC = I - m*C - C*(vn*Bn/(kn+Bn) + vi*Bi/(ki+Bi)),
                   dBn = cuen*vn*Bn*C/(kn+Bn) - hn*Bn,
                   dBi = cuei*vi*Bi*C/(ki+Bi) - hi*Bi)
       )
  return(list(ans))
}

runInvasions <- ddply(numParm.df, c('index'), function(xx){
  
  parm <- as.list(xx[, c('b', 'vmax', 'kmin', 'a', 'm', 'I')])
  
  parm$hn <- xx$h
  parm$hi <- xx$h
  
  cueCombo <- expand.grid(cuen=seq(1, 100, length=50)/100,
                          rel_cuei=rnorm(10, sd=0.1))
  cueCombo$cuei <- cueCombo$cuen+rnorm(nrow(cueCombo), sd=0.1)
  cueCombo <- cueCombo[cueCombo$cuei > 0,]
  
  cueCombo$vn <- with(parm, cue_v_tradeoff(b=b, vmax=vmax, cueCombo$cuen))
  cueCombo$kn <- with(parm, v_k_tradeoff(kmin=kmin, a=a, v=cueCombo$vn))
  
  cueCombo$vi <- with(parm, cue_v_tradeoff(b=b, vmax=vmax, cueCombo$cuei))
  cueCombo$ki <- with(parm, v_k_tradeoff(kmin=kmin, a=a, v=cueCombo$vi))
  
  invade.df <- ddply(cueCombo, c('cuen', 'cuei'), function(cuePairs){
    comboParm <- c(parm, cuePairs)
    preInvade <- with(comboParm, steadyState(b, vmax, kmin, a, h=hn, m, I, cue=cuen))
    if(all(preInvade > 0)){
      y0 <- list(C=preInvade$C, Bn=preInvade$B, Bi=preInvade$B*0.1)
      invasion <- tryCatch({lsoda(y=unlist(y0), times=c(1, 7, 30, 365, 365*10),
                                  func=compitition.model, parms=comboParm)},
                        warning = function(w){return(data.frame())},
                        error = function(e){return(data.frame())}
      )
      names(y0) <- paste(names(y0), '0', sep='')
      if(nrow(invasion) == 5){
        finalPools <- as.data.frame(c(comboParm, y0, as.list(invasion[nrow(invasion),])))
      }else{
        finalPools <- as.data.frame(comboParm)
      }
    }else{
      finalPools <- as.data.frame(comboParm)
    }
  })
  
  return(invade.df)
})

runInvasions <- ddply(runInvasions, c('index'), function(xx){
  ans <- steadyState_compete(b=xx$b, vmax=xx$vmax, kmin=xx$kmin, a=xx$a, m=xx$m, I=xx$I,
                             h=xx$hn, cue_i=xx$cuei, cue_n=xx$cuen)
  names(ans) <- c('C_ss', 'B_i_ss', 'B_n_ss')
  return(data.frame(xx, as.data.frame(ans)))
})
```
```{r plotValid}
temp <- merge(runInvasions, numParm.df, by='index')
ggplot(subset(temp, Bn > 0 & Bi > 0)) +
  geom_point(aes(x=cuen, y=cuei, color=Bn > Bi)) + 
  geom_vline(data=numParm.df, aes(xintercept=cue_strat), color='blue') +
  geom_vline(data=numParm.df, aes(xintercept=cue_opt), color='red') +
  labs(x='Native CUE', y='Invader CUE', title='Winner of 10 year invasion') +
  facet_wrap(~h+index)
```

#Numerical sketch book below

At steady state:
$C=\frac{I+\sum_i \frac{k_i h }{\epsilon_i}}{m+\sum_i v_i}$
If there are n identically parameterized pools then:
$C_n=\frac{I+n\frac{k h }{\epsilon}}{m+nv}$
Which is not the same as a single biomass pool
$C_1=\frac{I+\frac{k h }{\epsilon}}{m+v}$.

See below for a numerical example.
```{r}

runInvasions_ss <- ddply(numParm.df, c('index'), function(xx){
  
  parm <- as.list(xx[, c('b', 'vmax', 'kmin', 'a', 'm', 'I')])

  ans <- ddply(data.frame(cue=seq(0.1, 0.9, length=200)), c('cue'), function(yy){
    ans <- data.frame(cue_n=yy$cue, cue_i=yy$cue*rnorm(1, mean=1, sd=0.1))
    return(data.frame(ans,
                        as.data.frame(steadyState_compete(b=xx$b, 
                                                          vmax=xx$vmax, kmin=xx$kmin, 
                            a=xx$a, m=xx$m, h=xx$h, I=xx$I, 
                            cue_n=ans$cue_n, cue_i=ans$cue_i)
                        )))
  })
})

#merge(runInvasions_ss, numParm.df)
ggplot(subset(merge(runInvasions_ss, numParm.df), B_n > 0 & B_i > 0 & C > 0)) +
  geom_point(aes(x=cue_n, y=cue_i, color=B_n > B_i)) + 
  geom_vline(data=numParm.df, aes(xintercept=cue_strat)) + 
  labs(x='Native CUE', y='Invader CUE', title='Winner of 10 year invasion') +
  facet_wrap(~index+h)


test <- subset(numParm.df, index==2)
tradeoffs.df <- data.frame(cue=seq(0, 1, length=100),
                   v=cue_v_tradeoff(b=test$b, vmax=test$vmax, cue=seq(0, 1, length=100)),
                   k=v_k_tradeoff(kmin=test$kmin, a=test$a, 
                                  v=cue_v_tradeoff(b=test$b, vmax=test$vmax, 
                                                   cue=seq(0, 1, length=100))))

tradeoffs.df <- ddply(tradeoffs.df, c('cue', 'v', 'k'), function(xx){
  ans1 <- as.data.frame(steadyState(test$b, test$vmax, test$kmin, test$a, test$h, test$m, test$I, xx$cue))
  ans2 <- as.data.frame(steadyState_compete(test$b, test$vmax, test$kmin, test$a, test$h, test$m, test$I, xx$cue, xx$cue))
  names(ans2) <- sprintf('%s_compete', names(ans2))
  return(cbind(ans1, ans2))
})
ggplot(tradeoffs.df) + geom_point(aes(x=cue,y=cue*v/(B+k))) +
 geom_point(aes(x=cue,y=cue*v/(B_n_compete+k)), color='blue') +
  geom_vline(xintercept=test$cue_strat, color='red')

steadyState_compete(b=test$b, vmax=test$vmax, kmin=test$kmin, a=test$a, h=test$h, m=test$m,
                    I=test$I, cue_n=test$cue_strat, cue_i=test$cue_strat+0.02)
```

```{r timeEvol}
test <- subset(numParm.df, index ==2)
y0 <- list(C=test$C_opt, Bn=test$B_opt, Bi=test$B_opt*0.1)
comboParm <- c(test[1, c('b', 'vmax', 'kmin', 'a', 'm', 'I')],
               cuen=test$cue_opt,
               cuei=test$cue_opt,
               hn=test$h,
               hi=test$h)
comboParm <- c(comboParm,
               vn=cue_v_tradeoff(test$b, test$vmax, cue=comboParm$cuen),
               vi=cue_v_tradeoff(test$b, test$vmax, cue=comboParm$cuei))
comboParm <- c(comboParm,
               kn=v_k_tradeoff(test$kmin, test$a, v=comboParm$vn),
               ki=v_k_tradeoff(test$kmin, test$a, v=comboParm$vi))
carbonPools <- lsoda(y=unlist(y0), times=c(1:9, (1:9)*10, (1:9)*100, (1:9)*1e4),
                                  func=compitition.model, parms=comboParm)

ggplot(as.data.frame(carbonPools)) + 
  geom_line(aes(x=time, y=Bi), color='red') + 
  geom_line(aes(x=time, y=Bn), color='blue') + 
  geom_vline(xintercept=10*365) + geom_hline(yintercept=test$B_strat) + geom_hline(yintercept=test$B_opt, color='green') + 
  scale_x_log10()
```

```{r}
temp <- with(test, {
  cue <- seq(0, 1, length=100)
  v <- cue_v_tradeoff(b=b, vmax=vmax, cue)
  k <- v_k_tradeoff(kmin=kmin, a=a, v=v)
  
  ans <- steadyState_compete(b, vmax, kmin, a, h, m, I, cue_i=cue-0.005, cue_n=cue)
  
  measure <- cue*v/(k+ans$B_n)
  ans <- data.frame(cue, v, k, ans, measure)
  return(ans)
})

ggplot(temp) + geom_point(aes(x=cue, y=measure)) +  
  geom_vline(xintercept=test$cue_strat) + 
  geom_vline(xintercept=test$cue_opt, color='green') +
  geom_vline(aes(xintercept=cue[which.max(B_n)]), color='blue')

ggplot(temp) + geom_point(aes(x=cue, y=B_i)) + 
  geom_point(aes(x=cue, y=C), color='blue') + 
  geom_vline(xintercept=test$cue_strat) + 
  geom_vline(xintercept=test$cue_opt, color='green')

ggplot(subset(temp, B_n > 0 & B_i > 0)) + geom_point(aes(x=cue, y=B_n-B_i)) +
  geom_hline(yintercept=0) + geom_vline(aes(xintercept=cue[which.min(abs(B_n-B_i))])) +
  geom_vline(xintercept=test$cue_strat, color='red') + 
  geom_vline(xintercept=test$cue_opt, color='green')

ggplot(subset(merge(runInvasions_ss, numParm.df),
              index==test$index & B_n > 0 & B_i > 0 & C > 0)) +
  geom_point(aes(x=cue_n, y=cue_i, color=B_n > B_i)) + 
  geom_vline(data=subset(temp, B_n > 0 & B_i > 0), 
             aes(xintercept=cue[which.min(abs(B_n-B_i))])) + 
  labs(x='Native CUE', y='Invader CUE', title='Winner of 10 year invasion')
```
