---
title: "Primary Scratch"
author: "K Todd-Brown (ktoddbrown@gmail.com)"
date: "August 2, 2016"
output: html_document
---

WTS: Steady state for BESCP (JAM) models with constant inputs.

```{r libraries}
library(deSolve)
library(assertthat)
library(rootSolve)
library(plyr)
library(lhs)
library(ggplot2)
library(reshape2)
```
The full JAM model is defined below. 
$$\frac{dB}{dt} = \epsilon_{cue}U - D_B - P $$
$$\frac{dE}{dt} = P - D_E $$
$$\frac{dS}{dt} = I_S + M - U - R_s$$
$$\frac{dC}{dt} = I_C - M - R_c$$
$$\frac{dP_S}{dt} = R_s $$
$$\frac{dP_C}{dt} = R_c $$
Where $B$ is the microbial biomass, $E$ enzyme carbon mass, $S$ simple bioavailable carbon pool, $C$ complex non-bioavailable carbon pool, $P_S$ mineral sorbed simple carbon pool, and $P_C$ mineral sorbed complex carbon pool.
With rates: $U$ uptake kinetics (Monod: $U=\frac{vBS}{k+S}$), $D_B$ microbial death ($D_B=\frac{B}{\tau_B}$), $P$ enzyme production (Uptake driven: $P=pU$, Biomass drive: $P=pB$), enzyme turnover ($D_E = \frac{E}{\tau_E}$), $I_S$ inputs into simple carbon pool ($I_S=I\rho_s$), $I_C$ inputs to complex carbon pool ($I_C=I\rho_c$), $M$ conversion from complex to simple carbon (Michalious-Menten:$M=\frac{v_mEC}{k_m+C}$, reverse Michalius-Menten:$M=\frac{v_mEC}{k_m+E}$, multiplicative:$M=v_mEC$), $R_s$ mineral organic interaction for simple carbon ($R_s=\frac{S}{\tau_a}(1-\frac{P_S+P_C}{P_{sat}(P_S(t=0)+P_C(t=0))})-\frac{P_S}{\tau_d}$), and $R_c$  mineral organic interaction for complex carbon ($R_c=\frac{C}{\tau_a}(1-\frac{P_S+P_C}{P_{sat}(P_S(t=0)+P_C(t=0))})-\frac{P_C}{\tau_d}$).

At steady state to $\frac{dP_S}{dt}$ and $\frac{dP_C}{dt}$
$$0 = R_s= R_c$$

Extending ${dS}{dt}$ and ${dC}{dt}$
$$ 0 = I_S + M - U - R_s;  0 = I_C - M - R_c$$
$$ 0 = (I_S + M - U) + (I_C - M)$$
$$ 0 = I - U $$
$$ U = I $$

Extending $\frac{dE}{dt}$
$$0 = P - D_E$$
$$P = D_E$$

Extending $\frac{dB}{dt}$ and substituing the above relationships and allow $P = pU$
$$0 = \epsilon_{cue}U - D_B - P$$
$$0 = \epsilon_{cue}U - D_B - pU$$
$$0 = (\epsilon_{cue}-p) U - D_B$$
$$0 = (\epsilon_{cue}-p) I - \frac{B}{\tau_B}$$
$$B = I \tau_B (\epsilon_{cue}-p)$$

Recall $U=I$
$$\frac{vBS}{k+S} = I$$
$$\tau_B (\epsilon_{cue}-p) I \frac{vS}{k+S} = I$$
$$\tau_B (\epsilon_{cue}-p) \frac{vS}{k+S} = 1$$
$$\tau_B (\epsilon_{cue}-p) vS=k+S$$
$$[\tau_B (\epsilon_{cue}-p) v-1] S=k$$
$$S = \frac{k}{\tau_B (\epsilon_{cue}-p) v-1}$$

Recall $P = D_E$ and $U=I$
$$pU = \frac{E}{\tau_E}$$
$$E=Ip\tau_E$$

Recall $0 = I_C - M$
$$I_C=M$$
$$I\rho_c=\frac{v_mEC}{k_m+C}$$
$$I\rho_c=Ip\tau_E\frac{v_mC}{k_m+C}$$
$$k_m+C=\frac{p\tau_Ev_m}{\rho_c}C$$
$$k_m=(\frac{p\tau_Ev_m}{\rho_c}-1)C$$
$$k_m=\frac{p\tau_Ev_m-\rho_c}{\rho_c}C$$
$$C = \frac{k_m\rho_c}{p\tau_Ev_m-\rho_c}$$

Recall $0=R_s$; $0=R_c$. Let $P=P_s+P_c$
$$0=R_s+R_c$$
$$0=\frac{S+C}{\tau_a}(1-\frac{P}{P_{sat}})-\frac{P}{\tau_d}$$
$$0=\frac{S+C}{\tau_a}-\frac{P(S+C)}{\tau_a P_{sat}})-\frac{P}{\tau_d}$$
$$P(\frac{S+C}{\tau_aP_{sat}} + \frac{1}{\tau_d}) = \frac{S+C}{\tau_a}$$
$$ P (\frac{(S+C)\tau_d + \tau_a P_{sat}}{\tau_a P_{sat}\tau_d}) = \frac{S+C}{\tau_a}$$
$$ P (\frac{(S+C)\tau_d + \tau_a P_{sat}}{P_{sat}\tau_d}) = S+C$$
$$ P = (S+C) \frac{P_{sat}\tau_d}{(S+C)\tau_d + \tau_a P_{sat}}$$

Recall $0 = R_s$
$$0=\frac{S}{\tau_a}(1-\frac{P}{P_{sat}})-\frac{P_s}{\tau_d}$$
$$0=\frac{S}{\tau_a}(1-\frac{P}{P_{sat}})-\frac{P_s}{\tau_d}$$
$$\frac{P_s}{\tau_d}=\frac{S}{\tau_a}(1-\frac{P}{P_{sat}})$$
$$P_s=S\frac{\tau_d}{\tau_a}(1-\frac{P}{P_{sat}})$$

Similarlly
$$P_c=C\frac{\tau_d}{\tau_a}(1-\frac{P}{P_{sat}})$$

Overall:
$$B = I \tau_B (\epsilon_{cue}-p) $$
$$E = I p \tau_E $$
$$S = \frac{k}{\tau_B (\epsilon_{cue}-p) v - 1}$$
$$C = \frac{k_m \rho_c}{p \tau_E v_m - \rho_c}$$
$$P = (S+C) \frac{P_{sat}\tau_d}{(S+C)\tau_d + \tau_a P_{sat}}$$
$$P_s = S\frac{\tau_d}{\tau_a}(1-\frac{P}{P_{sat}})$$
$$P_c = C\frac{\tau_d}{\tau_a}(1-\frac{P}{P_{sat}})$$

```{r BECSP, eval=FALSE}
source('R/BECSP.R')
parms <- list(vmax_up=0.1, km_up=1, enz_prod=0.1, 
              vmax_enz=0.4, km_enz=2, cue=0.75, 
              enz_cost=sqrt(0.5)*0.9, 
              tau_B=100, tau_E=200, 
              P_sat=100, tau_a=1e4, tau_d=5e4,
              inputC=0.1, rho_c=0.7)
y0 <- unlist(list(B=0.8, E=0.1, S=0.5, C=10, P_S=100, P_C=100))
#temp <- dBECSP_dt(t=0, y=y0, parms)
SS <- stode(y=y0, func=dBECSP_dt, parms=parms, pos=TRUE)
SS_analytical <- SS_BECSP(parms)

print(SS)
print(SS_analytical)
```

```{r BECS}
source('R/BECS.R')
#Assert enz_cost 
with(parms, {sqrt(0.5) > enz_cost})
with(parms, {cat((2*enz_cost+1)*(1+enz_cost)/enz_cost); cue > (2*enz_cost-1)*(1+enz_cost)/enz_cost})

#Theoretical production rate
with(parms, {(enz_cost*cue-(1+enz_cost))/(2*(1+enz_cost)*enz_cost)})

enz_prodResponse <- adply(seq(0, sqrt(0.5), by=0.01), c(1), function(xx){
  parms$enz_prod <- xx
  ans <- SS_BECS(parms)
  return(data.frame(enz_prod=xx, B=ans$B, S=ans$S))
})

ggplot(enz_prodResponse) + geom_point(aes(x=enz_prod, y=B))
```

TODO: 
X 1) Calculate max from biomass from enz_prod variation from 0 to 1
2) Iterate through parameter space
3) Plot max biomass for parameter space

```{r sample, eval=FALSE}
parmRange <- read.csv('data/JAM_params.csv', stringsAsFactors=FALSE)
nameKey <- list(vmax_up='v_up', km_up='k_up', enz_prod='enz_prod', 
              vmax_enz='v_enz', km_enz='k_enz', cue='cue', 
              death='tau_B', E_turnover='tau_B', 
              enz_cost='enz_cost', inputC=NA)
nameKey <- data.frame(varName = names(nameKey), parameter = unlist(nameKey), stringsAsFactors=FALSE)
parmRange <- merge(nameKey, parmRange, all.x=TRUE)

parmRange[parmRange$varName %in% 'inputC', c('min', 'max')] <- c(1e-6, 2.7e-4) #from NPP range of 0 to 6.5 g m^-3 day^-1 of global NPP
parmRange[parmRange$varName %in% 'inputC', c('unit')] <- 'kg-C m^-3-soil hr^-1'

parmRange <- parmRange[parmRange$varName %in% c('enz_prod', 'km_up', 'vmax_up', 'death', 'cue', 'inputC'),]

sampleNum <- 100
unifSample <- as.data.frame(improvedLHS(sampleNum, dim(parmRange)[1]))
names(unifSample) <- parmRange$varName
unifSample$index <- 1:sampleNum

trueSample <- ddply(unifSample, c('index'), function(xx){
  parSet <- xx[parmRange$varName]
  ans <- as.list(exp(log(parmRange$min) + 
                       log(parmRange$max / parmRange$min) * unlist(parSet)))
  return(as.data.frame(ans))
})

runSample <- ddply(trueSample, c('index'), function(xx){
  ans <- xx[parmRange$varName]
  temp <- SS_BECS(ans)
  ans$B <- temp$B
  ans$S <- temp$S
  if(all(temp > 0)){
    ans$maxB <- max_Bs_BECS(ans)
  }else{
    ans$maxB <- NA
  }
})

ggplot(trueSample) + geom_point(aes(x=B, y=S))

summary(with(trueSample, {(1-enz_prod)/(cue-enz_prod) < 1}))
summary(with(trueSample, {death*vmax_up*(cue-enz_prod)}))

unifSample <- merge(unifSample, trueSample[,c('index', 'maxB')])
plot.df <- melt(unifSample, id.vars=c('index', 'maxB'))
ggplot(plot.df) + geom_histogram(aes(x=value, fill=is.finite(maxB))) + facet_wrap(~variable)

pairs(subset(unifSample, is.finite(maxB), select=c("cue", "km_up", "death", "vmax_up", "inputC", 'enz_prod')))
```

```{r BE, eval=FALSE}
source('R/BE.R')
y0 <- c(B=28, E=1.4)
ans <- data.frame()
for(p in seq(0, 1, by=0.01)){
parms <- list(cue=0.5, tau_B=5000, tau_E=1000, p=p, v=0.0277, k=0.3)

SS <- stode(y=y0, func=dBE_dt, parms=parms)
ans <- rbind(ans, data.frame(type='stode', p=p, B=SS$y[1], E=SS$y[2]))

SS <- BE_SS(parms)
ans <- rbind(ans, data.frame(type='analytical', p=p, B=SS$B, E=SS$E))
}
ggplot(ans) + geom_line(aes(x=p, y=B)) + facet_wrap(~type, scale='free')


```

```{r BEC, eval=FALSE}
source('R/BEC.R')
y0 <- c(B=28, E=1.4, C=10)
parms <- list(cue=0.5, tau_B=85, tau_E=10, p=0.1, v=0.01, k=0.3, input=0.1)
SS <- stode(y=y0, func=dBEC_dt, parms=parms)
#temp <- lsoda(times=seq(0, 1e4), y=y0, func=dBEC_dt, parms=parms)

ans <- data.frame()
for(p in seq(0, 1, by=0.01)){
parms$p <- p
SS <- stode(y=y0, func=dBEC_dt, parms=parms)
ans <- rbind(ans, data.frame(type='stode', p=p, B=SS$y[1], E=SS$y[2]))

}
ggplot(ans) + geom_line(aes(x=p, y=B)) + facet_wrap(~type, scale='free')

```
